%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0.10pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Rexford}{Aboagye}{ 
\href{mailto:rexfordnana@gmail.com}{rexfordnana@gmail.com} | 240.756.3189
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t][18cm]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Delaware State University}
\descript{MS in Computer Science}
\descript{Machine Learning / Data Analytics}
\location{December 2016 | Dover, DE}
\sectionsep

\subsection{University of Ghana}
\descript{BS in Computer Science}
\descript{BA in Economics}
\location{June 2011 | Accra, Ghana}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/rexfordnana}{\bf rexfordnana} \\
LinkedIn://  \href{https://www.linkedin.com/in/rexfordnana}{\bf rexfordnana} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Areas of Study}
Machine Learning \& Data Analytics \\
Networks \& Distributed Systems \\
Pattern Recognition \\
Database Systems \\
IOT \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Production:}
NodeJS \textbullet{} Python \\
JAVA \textbullet{} Bash \\
 SQL \textbf{•} CypherShell \\
\location{Familiar:}
C \textbullet{} PHP \\
C++ \textbullet{} \LaTeX\
\sectionsep

\subsection{Software}
\location{Infrastructure and Deployment:}
AWS \textbullet{} ConcourseCI \textbullet{} Neo4J \\
Jenkins \textbullet{} MongoDB\\
\location{Other:}
Git \textbullet{} Ansible \\
Terraform
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t][18cm]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Comcast}
\descript{| Software Engineer }
\location{February 2019 – Present | Philadelphia, PA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and built an integration solution between GraphQL API and a REST that helped streamline the internal process of partner creation in NodeJS using serverless.
\item Designed and implemented a subscription based notification system using a serverless architecture and python that increased downstream clients data consistency by 99\%
\item Created smart alerts on internal applications that gave the team operational visibility into all running systems.
\item Contributed to CRUD API creation in both NodeJS (Express) and Java (SpringBoot)
\item Automated the deployment of code infrastructure using Terraform and Terragrunt

\end{tightemize}
\sectionsep

\runsubsection{Barclays US}
\descript{| Software Engineer }
\location{February 2017 – February 2019 | Wilmington, DE}

\begin{tightemize}
\item Development of REST APIs that interact with Legacy SOAP services and returns JSON format data to ReactJS library using SpringBoot(JAVA).
\item Creation of REST API and Microservices automation framework using REST assured libraries and Karate IO.
\item Configuring Dockerfiles to create immutable virtual images for easy deployments.
\item Maintain GIT branches during project development. Conducting merges and use MAVEN for building and deploying application to APAAS( Cloud Environment)

\end{tightemize}
\sectionsep

\runsubsection{United Nations}
\descript{| Java Developer }
\location{Jan 2016 – Dec 2016 | New York, NY}
\begin{tightemize}
\item Designed and develop a full stack application to search archives and telephone notes of the UN Secretary General.
\item Involvement in all phases of Software Development life cycle including maintenance and support 
\item Creation of CICD pipeline for individual MCA's(Multi Channel Application) using GOCD.
\item  Creation of a friendly web User Interface for Admin users to easily review OCR'd archives in Python
\item Performing data validation on SQL server
\end{tightemize}
\sectionsep

\runsubsection{Embassy Of Ghana}
\descript{| Software Engineer}
\location{September 2013 – January 2016 | Washington, DC}
\begin{tightemize}
\item Primarily a data, backend engineer. Managed an
intern, conducted interviews, and involved in recruiting.
\item Responsible for understanding agency requirements for various projects by interacting with different team members.
\item Developed a Django web portal for visa applications and passport renewal forms
\item Monitoring Application logs in Kibana and Openshift.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}
\end{document}  \documentclass[]{article}
